
\section{Conclusions}
\begin{itemize}
    \item The theoretical Ball-and-Plate System (BPS) model were established and simulated, they shown promising results. The experimental implementation and testing, were less quality by the lack of adequate hardware, mainly the rods and actuators, however it still do a very good functional work 
    
    \item The BPS presents an ideal platform for control engineering students to experiment with and validate control methodologies. This is attributed to the system's cost-effectiveness and the ease with which the response can be visually observed, making it a practical and insightful tool for educational purposes.

    \item Software and programming for controlling any system is as important as theoretical control analysis, which can be an issue when approaching the challenge of building a system from an exclusive theoretical background.

    \item PID controllers remain one of the most widely employed feedback controllers. They operate by calculating an error value, representing the difference between a measured process variable and a desired set point. The controller aims to minimize this error by making adjustments to the process control inputs. However, it's important to note that PID controllers have limitations when it comes to rapidly stabilizing and mitigating the impact of disturbances  
\end{itemize}

\section{Future Work}
Numerous ways for enhancing both the plant design and controller performance are available for exploration

\begin{itemize}
    \item While the study relied on the resistive touchscreen for data acquisition, integrating a top camera could offer a more suitable solution. The touch screen, despite filtering efforts, exhibited intolerable noise and discontinuities in readings. Transitioning to a camera-based approach presents a promising alternative for precise ball position determination.

    \item  More advanced control algorithms can be explored such as Model Predictive Control (MPC), Optimal Control (LQR) or  Adaptive Control, to potentially achieve superior system stability and performance.


\end{itemize}
